---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# altRnative

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/ismailsunni/altRnative.svg?branch=master)](https://travis-ci.org/ismailsunni/altRnative)
<!-- badges: end -->

An R package to run you R code in different R implementations and platforms in [Docker]() containers.

## Installation

You can install the development version [from GitHub](https://github.com/ismailsunni/altRnative) with:

``` r
# install.packages("remotes")
remotes::install_github("ismailsunni/altRnative")
```
## Example

```{r example, cache=TRUE, results='hide', fig.width=8}
library('altRnative')
pull_docker_image(c('gnu-r', 'mro'), c('debian', 'ubuntu', 'fedora'))

benchmark_result = benchmarks_code(
  code = "1 + 1", 
  r_implementations = c('gnu-r', 'mro'), 
  platforms = c('debian', 'ubuntu', 'fedora', 'archlinux'),
  times = 3
  )

library('ggplot2')
autoplot(benchmark_result)
```

## Contribute

Please note that the 'altRnative' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
  
## License

This project is published under MIT license, see file `LICENSE`.
