---
title: "Geospatial Benchmark"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{benchmark}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
IS_EVAL = FALSE
```

This vignette explain about the steps that is taken to do benchmark for geospatial workfflow across different combination of R implementation and operating system and platform using `altRnative` R package.

To load the package, run this command:

```{r setup}
library(altRnative)
```

Since this package is using docker image, there is a function to pull the needed docker images:

```{r pull_image, message='hide', results=FALSE, eval=IS_EVAL}
pull_docker_image(c('gnu-r', 'mro'), c('debian', 'ubuntu', 'fedora'))
```

You can also specify the pulling in the `benchmark_code` function by adding `pull_image` parameter and set it to `TRUE`. The default value is `FALSE` since mostly you only need to run it once.

First, we will check that the package is working properly by running very simple code (e.g. `1+1`).

```{r simple_check, message='hide', results=FALSE, eval=IS_EVAL}
benchmark_result = benchmarks_code(
  code = "1 + 1", 
  r_implementations = c('gnu-r', 'mro'), 
  platforms = c('debian', 'ubuntu', 'fedora', 'archlinux'),
  times = 10
  )
```

The result is a micorbenchmark object that can be printed or create the graph (using `ggplot2`)
```{r simple_result, eval=IS_EVAL}
print(benchmark_result)
library('ggplot2')
autoplot(benchmark_result)
```

Next, we use Spatial Data Science with R book from Prof. Edzer Pebesma as the code for geospatial benchmark. I have modified the book to remove the part that using `stars` data and Air Quality data since both are very big. The modified book can be obtained from [my fork on Github](https://github.com/ismailsunni/sdsr). You can eithe download or clone using git to your local machine.

```{bash clone_book, eval=FALSE}
cd /home/ismailsunni/dev/r
git clone git@github.com:ismailsunni/sdsr.git
```

After that you can open an R session and run the benchmark. First you need to define the R code/script that will be benchmarked. In this case, you need to set the working directory to mapped directory inside the container (e.g. `/home/docker/sdsr`). Cleaning the cache and removing old result is needed also since it will disturb the benchmarking process. Lastly, `render_book` will run all the code in the book and render it.
```{R sdsr_code, eval=IS_EVAL}
code = expression(
  setwd('/home/docker/sdsr'), 
  bookdown::clean_book(TRUE), 
  unlink('_book/', recursive=TRUE), 
  unlink('_bookdown_files', recursive=TRUE), 
  bookdown::render_book('index.Rmd', 'bookdown::gitbook')
  )
```
In this step, you will run the benchmark using the previous `code` as input. Please note that the `volumes` in the `benchmark_code` function is mapped from your `sdsr` directory. In my case, it is `/home/ismailsunni/dev/r/sdsr`. Other arguments are `platforms` and `r_implementations` to set the platform and R implementations of the docker containers. Lastly, `times` argument is used to specify how many times the code needs to be run in the benchmark process.
```{R sdsr_benchmark, eval=IS_EVAL}
sdsr_result = benchmarks_code(
  code = code, 
  platforms = c('debian', 'ubuntu', 'fedora', 'archlinux'),
  r_implementations = c('gnu-r', 'mro'), 
  volumes = '/home/ismailsunni/dev/r/sdsr:/home/docker/sdsr', 
  times = 3
  )
```

From here, you can see the result or plot the graph like the previous result.
```{r sdsr_result, eval=IS_EVAL}
print(sdsr_result)
autoplot(sdsr_result)
```

## Running Benchmark Per Chapter

We have added a script to extract the R code for all chapter in the SDSR book in this fork. If you updated the book, you can run `Rscript extract_sdsr_code.R`. Here we will show how to run benchmark for each chapter of SDSR.
```{r chapter_benchmark, eval=IS_EVAL, message='hide', results=FALSE}
# Commented entries do not have any code.
chapters = c(
    '01-hello.R',
    '02-Spaces.R',
    '03-Geometries.R',
    '04-Raster-Cube.R',
    '05-GeomManipulations.R',
    '06-Attributes.R',
    '07-ReferenceSystems.R',
    '08-Plotting.R',
    '09-BasePlot.R',
    '10-Ggplot2.R',
    # Files below do not have files
    # '11-Interactive.R',
    # '12-SummarizingGeoms.R',
    # '13-PointPattern.R',
    # '14-Manipulating.R',
    # '15-UpDownscaling.R',
    # '16-Geostatistics.R',
    # '17-Areal.R',
    # '18-SpatialRegression.R',
    # '19-Movement.R',
    # '20-STModelling.R',
    # '30-sp-raster.R',
    '98-rbascis.R'
)

benchmark_result <- c()

for (chapter in chapters){
    code = substitute(
      expression(
        setwd('/home/docker/sdsr/code'), 
        source(chapter)), 
      list(chapter = chapter))
    print(code)
    chapter_result = benchmarks_code(
      code = code,
      platforms = c('debian', 'ubuntu', 'fedora', 'archlinux'),
      r_implementations = c('gnu-r', 'mro'),
      volumes = '/home/ismailsunni/dev/r/sdsr:/home/docker/sdsr',
      times = 10
    )
    # append
    benchmark_result[[chapter]] = chapter_result
}
```

And save the box plot in the disk.
```{r save_chapter_code_benchmark_plot, eval=IS_EVAL, message='hide', results=FALSE}
# Save plot as image
for (chapter in chapters){
  chapter_result = benchmark_result[chapter]
  filename = paste0('./plots/', substr(chapter, 0, nchar(chapter) - 1), 'png')
  print(filename)
  png(filename=filename, width = 800, height = 400)
  boxplot(
    chapter_result[[1]], 
    log = FALSE, 
    ylim = c(0, ceiling(max(chapter_result[[1]][[2]]) / 1000000000 * 1.1)),
    xlab = 'Docker Images',
    ylab = 'Duration (seconds)',
    main = chapter
    )
  dev.off()
}
```

For running all the code in one run you can run the `sdsr.R` file only.

```{r sdsr_code_benchmark, eval=IS_EVAL, message='hide', results=FALSE}
    sdsr_code = expression(setwd('/home/docker/sdsr/code'), source('sdsr.R'))
    print(sdsr_code)
    sdsr_code_benchmark_result = benchmarks_code(
      code = sdsr_code,
      platforms = c('debian', 'ubuntu', 'fedora', 'archlinux'),
      r_implementations = c('gnu-r', 'mro'),
      volumes = '/home/ismailsunni/dev/r/sdsr:/home/docker/sdsr',
      times = 10
    )
```

And save the box plot in the disk.
```{r save_sdsr_code_benchmark_plot, eval=IS_EVAL, message='hide', results=FALSE}
  filename = paste0('./plots/sdsr.png')
  print(filename)
  png(filename=filename, width = 800, height = 400)
  boxplot(
    sdsr_code_benchmark_result, 
    log = FALSE, 
    ylim = c(0, ceiling(max(sdsr_code_benchmark_result[[2]]) / 1000000000 * 1.1)),
    xlab = 'Docker Images',
    ylab = 'Duration (seconds)',
    main = 'All SDSR Code '
    )
  dev.off()
```

